Replication of \"Anti-Immigrant Rhetoric and ICE Reporting Interest: Evidence

### 2024-06-28 paper_replication_buka.Rmd
buka's file after finishing

>>>>

ice <-
  read_csv("ice_reportings.csv", skip = 4, col_names = c("year", "month", "reports", "reports_convicted", "", "", "", "reports_non_criminal", "", "")) %>%
  select(c(1, 2, 3, 4, 8)) %>%
  fill(year, .direction = "down") %>% 
  filter(month != "Total") %>%
  mutate(
    month = match(month, month.name),
    date = make_date(year, month)
  )

```{r}
ice_report_w_election <- 
  ice |>
  filter(date <= '2020-01-01') |> 
  rename( year_month = date) |>
  # select(year_month, year, month, president, immigr_report ) |>
  arrange(year_month) |>
  left_join(time_lines, by = "year_month") |>
  fill(time, .direction = c("down")) |>  view()

head(ice_report_w_election)
```

ice_report_w_election %>%
  ggplot(aes(x = year_month, y = reports, colour = time)) + 
  geom_point() +
  geom_smooth(se=FALSE) +
  geom_vline(data = time_lines, aes(xintercept = as.numeric(year_month)), linetype = "dotted", color = "black") +
  xlab("Month") +
  ylab("Arrests") +
  ggtitle("Total Immigration-Related Arrests By Month")

ice_report_w_election %>%
  ggplot(aes(x = year_month, y = reports_convicted, colour = time)) + 
  geom_point() +
  geom_smooth(se=FALSE) +
  geom_vline(data = time_lines, aes(xintercept = as.numeric(year_month)), linetype = "dotted", color = "black") +
  xlab("Month") +
  ylab("Arrests") +
  ggtitle("Arrested Immigrants Who Were Actually Convicts By Month")

ice_report_w_election %>%
  ggplot(aes(x = year_month, y = reports_non_criminal, colour = time)) + 
  geom_point() +
  geom_smooth(se=FALSE) +
  geom_vline(data = time_lines, aes(xintercept = as.numeric(year_month)), linetype = "dotted", color = "black") +
  xlab("Month") +
  ylab("Arrests") +
  ggtitle("Arrested Immigrants Who Were Not Convicts By Month")

The paper suggests that anti-immigrant searches likely result in actual ICE denunciations and that an increase in media coverage of anti-immigrant topics was correlated with an increase in searches. They show higher rates of coverage during Trumps campaign and post-inauguration. We expected the number of immigrant arrests to follow a similar pattern, but using data from the Department of Homeland Security, we observe higher amounts of arrests pre-campaign, a lower number during the campaign, then a spike in numbers post-inauguration.
